---
title: "Divergence_outliers"
author: "E. Oziolor"
date: "April 30, 2018"
output: html_document
---

#Re-do of outlier window pipeline for divergence with Hudson estimator of Fst

## grabbing calculated PBS over 1kb regions and repeating merging outlier windows

```{r}

library(XML)
library(tidyr)
library(stringr)
library(dplyr)
library(gtools)
library(naturalsort)
library(RCurl)
library(ggplot2)
library(reshape2)

load("~/analysis/data/comparison/noah_stats.RData") #loading data produced from individual SNP call pi and dxy calculations
pbstat2<-cbind(lift[,1:3],pbstat[,4:6],pbstat[,8],pbstat[,7]) #Binding pbs statistics for populations of interest, in this case F. grandis 

#Only run if you haven't created an ordered table of chromosomes
#r=ordering them by chromosome
# ord<-mixedorder(pbstat2$V1) #Data imported is ordered alphabetically (ex. chr1, chr10...); this reorders it to alphanumeric (chr1, chr2...)
# pbsn<-pbstat2[ord,] #applying sorted order to our dataset
# 
# pbsn$V1<-factor(pbsn$V1,levels=c("chr1","chr2","chr3","chr4","chr5","chr6","chr7","chr8","chr9","chr10",
#                                      "chr11","chr12","chr13","chr14","chr15","chr16","chr17","chr18","chr19",
#                                      "chr20","chr21","chr22","chr23","chr24")) #factors are sometimes not sorted together with it, so sorting them separately
# 
# #writing table to be used in further analysis
# write.table(pbsn[,1:8],"~/analysis/data/fst/hudsonpbs_1kb.bed",row.names = FALSE,col.names = FALSE,quote=FALSE,sep='\t') #Not really necessary, but subsetting the data, so that you don't have to reorder every time

#reading in pbs table to find outlier regions
pbs<-read.table("~/analysis/data/fst/hudsonpbs_1kb.bed",header=FALSE) #loading in ordered table of pbs values for populations of interest
pbsname<-c("Scaf","start","end","BBpbs","VBpbs","PBpbs","SJpbs","BNPpbs") #naming them according to their belonging
colnames(pbs)<-pbsname #applying naming scheme

quantiles<-c() #calculating quantiles in order to apply outlier thresholds
for(i in 1:5){
  quantiles[i]<-quantile(pbs[,i+3],probs=.99,na.rm=TRUE)
}


# Quantile info
# BBpbs - 0.18202835
# VBpbs - 0.14889788 
# PBpbs - 0.22912063 
# SJpbs - 0.08587848
# BNP - 0.04271162


```

## Using bedtools to merge outliers of these pbs statistics; removing non-mapped regions (noise for the most part)

```{bash}
#grabbing the table file (remember that it needs to be in bed format);
cat ~/analysis/data/fst/hudsonpbs_1kb.bed | \
#removing all NA
grep -v NA | \
#using awk to remove all values below outlier
awk '$4>0.18202835 || $5>0.14889788  || $6>0.22912063 || $7>0.08587848 || $8>0.04271162' | \
#piping into bedtools and merging into outlier windows within 50000 of each other
~/program/bedtools2/bin/bedtools merge -i stdin -d 50000 \
#which columns do you want summary statistics printed for
-c 4,4,5,5,6,6,7,7,8,8 \
#what statistics do you want printed
-o sum,count,sum,count,sum,count,sum,count,sum,count \
#using fai file to map those regions back to genomic regions and saving as bed file
-g <(cut -f 1-2 ~/analysis/data/genome/unsplit_merge.fasta.fai) > ~/analysis/data/fst/hudson_pbsmergeoutliers.bed

#doing the same but instead with summed statistic, with highest peak outliers
cat ~/analysis/data/fst/hudsonpbs_1kb.bed | \
grep -v NA | \
awk '$4>0.18202835 || $5>0.14889788  || $6>0.22912063 || $7>0.08587848 || $8>0.04271162' | \
~/program/bedtools2/bin/bedtools merge -i stdin -d 50000 \
-c 4,4,5,5,6,6,7,7,8,8 \
-o max,count,max,count,max,count,max,count,max,count \
-g <(cut -f 1-2 ~/analysis/data/genome/unsplit_merge.fasta.fai) > ~/analysis/data/fst/hudson_pbsmergeoutliers_max.bed

```

## Now taking these merged windows and plotting them to find common outliers

```{r}
PBSout<-read.table("~/analysis/data/fst/hudson_pbsmergeoutliers.bed",stringsAsFactors=FALSE) # Reading in the maximum outlier regions of interest
colnames(PBSout)<- c("Scaf","start","end","BBsum", "BBcount","VBsum","VBcount","PBsum","PBcount","SJsum","SJcount","BNPsum","BNPcount") #assigning them column names (we chose columns to be printed earlier)

BBtot<-sum(PBSout[,4]) #summing total level of divergence in these regions
VBtot<-sum(PBSout[,6])
PBtot<-sum(PBSout[,8])
SJtot<-sum(PBSout[,10])
BNPtot<-sum(PBSout[,12])

interest2<-c() #creating a vector of interest to weigh in the level of divergence by population, so that ones in most divergent populations don't get outweighed
for (i in 1:2119){
  interest2<-(PBSout[,4]/BBtot)*100+(PBSout[,6]/VBtot)*100+(PBSout[,8]/PBtot)*100+(PBSout[,10]/SJtot)*100+(PBSout[,12]/BNPtot)*100
}

ord<-order(interest2,decreasing=TRUE) #order that vector
ord2<-ord[1:10] #show top10 regions

par(mar=c(4.2,5,4,4)) #plotting these outliers
plot(PBSout[ord2,"BBsum"],col='black',pch=20,cex=3,ylim=c(0,4000),ylab="Level of divergence",xlab="Region number",
     cex.lab=2,cex.axis=2)
points(PBSout[ord2,"VBsum"],col='grey',pch=20,cex=3)
points(PBSout[ord2,"PBsum"],col='red',pch=20,cex=3)
points(PBSout[ord2,"SJsum"],col='darkorange',pch=20,cex=3)
points(PBSout[ord2,"BNPsum"],col="gold",pch=20,cex=3)

legend('topright',legend=c("BB","VB","PB","SJ","BNP"),col=c("black","grey","red","darkorange2","gold"),
       pch=20,cex=2,bty="n",y.intersp=1,x.intersp=.5)

```

## Grabbing those regions and putting them on pbs plots

```{r}
pbs<-read.table("~/analysis/data/fst/hudsonpbs_1kb.bed",header=FALSE,stringsAsFactors = FALSE) #reading in the windowed pbs estimates
pbsname<-c("Scaf","start","end","BBpbs","VBpbs","PBpbs","SJpbs","BNPpbs") #naming columns
colnames(pbs)<-pbsname

col<-c()# finding 1% outliers
for (i in 1:5){
  col[i]<-quantile(pbs[,i+3],prob=.99,na.rm=TRUE)
}

pbsc<-pbs %>% filter(str_detect(Scaf,"chr")) #only selecting chromosomes

#removing the crappy scaffold that has the first 141 windows of chromosome 16 (mismapped from chr1); this is discovered in dxy.r script in introgression folder
chr16<-str_detect(pbsc$Scaf,"chr16") #grab chr16
ord<-order(pbsc[chr16,"BBpbs"],decreasing=TRUE) #pick highest value of chr16
pbsc16<-pbsc[chr16,] #make an object
chr16rows<-as.numeric(rownames(pbsc[chr16,])) #grab rownames for it
crappyrows<-chr16rows[1:300] #get the first 141 rows which contain scaffold "crappy"
pbsct<-pbsc[-c(crappyrows),] #remove thos rows from total
chr16.2<-str_detect(pbsc$Scaf,"chr16") #do it again
head(pbsct[chr16,])
pbsc<-pbsct
head(pbsc[chr16,])

#Grabbing regions that are put together pretty well/widely----
pbs_out_temp<-read.table("~/analysis/data/fst/hudson_pbsmergeoutliers_max.bed",stringsAsFactors = FALSE) #loads a pbs vector with windows merged within 50kb of each other and with max and windows count statistics
names<-c("Scaf","start","end","BBmax","BBcount","VBmax","VBcount","PBmax","PBcount","SJmax","SJcount","BNPmax","BNPcount")
colnames(pbs_out_temp)<-names

pbs_out<-pbs_out_temp %>% filter(str_detect(Scaf,"chr")) #selecting only chromosome mapped scaffolds

#checking for whether those are outliers in different groups--------
all<-pbs_out[,4]>col[1] & pbs_out[,6]>col[2] & pbs_out[,8]>col[3] & pbs_out[,10]>col[4] & pbs_out[,12]>col[5]
res<-pbs_out[,4]>col[1] & pbs_out[,6]>col[2] & pbs_out[,8]>col[3] & pbs_out[,10]<col[4] & pbs_out[,12]<col[5]
interm<-pbs_out[,4]<col[1] & pbs_out[,6]<col[2] & pbs_out[,8]<col[3] & pbs_out[,10]>col[4] & pbs_out[,12]>col[5]
bbu<-pbs_out[,4]>col[1] & pbs_out[,6]<col[2] & pbs_out[,8]<col[3] & pbs_out[,10]<col[4] & pbs_out[,12]<col[5]
vbu<-pbs_out[,4]<col[1] & pbs_out[,6]>col[2] & pbs_out[,8]<col[3] & pbs_out[,10]<col[4] & pbs_out[,12]<col[5]
pbu<-pbs_out[,4]<col[1] & pbs_out[,6]<col[2] & pbs_out[,8]>col[3] & pbs_out[,10]<col[4] & pbs_out[,12]<col[5]
sju<-pbs_out[,4]<col[1] & pbs_out[,6]<col[2] & pbs_out[,8]<col[3] & pbs_out[,10]>col[4] & pbs_out[,12]<col[5]
bnpu<-pbs_out[,4]<col[1] & pbs_out[,6]<col[2] & pbs_out[,8]<col[3] & pbs_out[,10]<col[4] & pbs_out[,12]>col[5]

write.table(pbsc[,1:3],"~/analysis/data/fst/subsample/PBS_keep_1kb.bed",
            row.names = FALSE,col.names = FALSE,quote=FALSE,sep="\t")
write.table(pbs_out[all,1:3],"~/analysis/data/fst/subsample/pbs_regions_sharedall.bed",
            row.names = FALSE,col.names = FALSE,quote = FALSE, sep="\t")
write.table(pbs_out[res,1:3],"~/analysis/data/fst/subsample/pbs_regions_sharedres.bed",
            row.names = FALSE,col.names = FALSE,quote = FALSE, sep="\t")
write.table(pbs_out[interm,1:3],"~/analysis/data/fst/subsample/pbs_regions_sharedinterm.bed",
            row.names = FALSE,col.names = FALSE,quote = FALSE, sep="\t")
write.table(pbs_out[bbu,1:3],"~/analysis/data/fst/subsample/pbs_regions_sharedbbu.bed",
            row.names = FALSE,col.names = FALSE,quote = FALSE, sep="\t")
write.table(pbs_out[vbu,1:3],"~/analysis/data/fst/subsample/pbs_regions_sharedvbu.bed",
            row.names = FALSE,col.names = FALSE,quote = FALSE, sep="\t")
write.table(pbs_out[pbu,1:3],"~/analysis/data/fst/subsample/pbs_regions_sharedpbu.bed",
            row.names = FALSE,col.names = FALSE,quote = FALSE, sep="\t")
write.table(pbs_out[sju,1:3],"~/analysis/data/fst/subsample/pbs_regions_sharedsju.bed",
            row.names = FALSE,col.names = FALSE,quote = FALSE, sep="\t")
write.table(pbs_out[bnpu,1:3],"~/analysis/data/fst/subsample/pbs_regions_sharedbnpu.bed",
            row.names = FALSE,col.names = FALSE,quote = FALSE, sep="\t")


#source("http://bioconductor.org/biocLite.R")
#biocLite()
#biocLite('rtracklayer')

#Finding the overlaps in full data---------
library("rtracklayer")

bed1=import("~/analysis/data/fst/subsample/PBS_keep_1kb.bed") #importing the windows in which we are searching

bedall=import("~/analysis/data/fst/subsample/pbs_regions_sharedall.bed") #importing shared outliers
bed1overlall=bed1[bed1 %over% bedall] #Making overlapping regions into genome file
hitsall<-findOverlaps(bedall,bed1) #finding overlaps as hits
allhit<-subjectHits(hitsall) #making them into a true false vector

#same for the rest of the comparisons
bedres=import("~/analysis/data/fst/subsample/pbs_regions_sharedres.bed")
bed1overlres=bed1[bed1 %over% bedres]
hitsres<-findOverlaps(bedres,bed1)
reshit<-subjectHits(hitsres)

bedinterm=import("~/analysis/data/fst/subsample/pbs_regions_sharedinterm.bed")
bed1overlinterm=bed1[bed1 %over% bedinterm]
hitsinterm<-findOverlaps(bedinterm,bed1)
intermhit<-subjectHits(hitsinterm)

bedbbu=import("~/analysis/data/fst/subsample/pbs_regions_sharedbbu.bed")
bed1overlbbu=bed1[bed1 %over% bedbbu]
hitsbbu<-findOverlaps(bedbbu,bed1)
bbuhit<-subjectHits(hitsbbu)

bedvbu=import("~/analysis/data/fst/subsample/pbs_regions_sharedvbu.bed")
bed1overlvbu=bed1[bed1 %over% bedvbu]
hitsvbu<-findOverlaps(bedvbu,bed1)
vbuhit<-subjectHits(hitsvbu)

bedpbu=import("~/analysis/data/fst/subsample/pbs_regions_sharedpbu.bed")
bed1overlpbu=bed1[bed1 %over% bedpbu]
hitspbu<-findOverlaps(bedpbu,bed1)
pbuhit<-subjectHits(hitspbu)

bedsju=import("~/analysis/data/fst/subsample/pbs_regions_sharedsju.bed")
bed1overlsju=bed1[bed1 %over% bedsju]
hitssju<-findOverlaps(bedsju,bed1)
sjuhit<-subjectHits(hitssju)

bedbnpu=import("~/analysis/data/fst/subsample/pbs_regions_sharedbnpu.bed")
bed1overlbnpu=bed1[bed1 %over% bedbnpu]
hitsbnpu<-findOverlaps(bedbnpu,bed1)
bnpuhit<-subjectHits(hitsbnpu)

pbsc<-cbind(pbsc,0,0,0,0,0,0,0,0) #adding columns to the dataframe of pbs values
newn<-c("Scaf","start","end","BB","VB","PB","SJ","BNP","all","res","interm","bbu","vbu","pbu","sju","bnpu") #giving them names
colnames(pbsc)<-newn
pbsc[allhit,"all"]<-pbsc[allhit,"all"]+1 #adding 1s for true values in hits parameter
pbsc[reshit,"res"]<-pbsc[reshit,"res"]+1
pbsc[intermhit,"interm"]<-pbsc[intermhit,"interm"]+1
pbsc[bbuhit,"bbu"]<-pbsc[bbuhit,"bbu"]+1
pbsc[vbuhit,"vbu"]<-pbsc[vbuhit,"vbu"]+1
pbsc[pbuhit,"pbu"]<-pbsc[pbuhit,"pbu"]+1
pbsc[sjuhit,"sju"]<-pbsc[sjuhit,"sju"]+1
pbsc[bnpuhit,"bnpu"]<-pbsc[bnpuhit,"bnpu"]+1

#plotting those results by using the pbs_out vector-------------
pbsc$Scaf<-factor(pbsc$Scaf,levels=c("chr1","chr2","chr3","chr4","chr5","chr6","chr7","chr8","chr9","chr10",
                                     "chr11","chr12","chr13","chr14","chr15","chr16","chr17","chr18","chr19",
                                     "chr20","chr21","chr22","chr23","chr24")) #ordering factor levels
palette(c("grey40","grey80"))
par(mfrow=c(5,1),mar=c(0,3,0,0))
plot(pbsc[,4],pch=20,cex=1.2,
     col=ifelse(pbsc[,"all"]>0,"purple",
                ifelse(pbsc[,"res"]>0,"black",
                       ifelse(pbsc[,"interm"]>0,"firebrick2",
                              ifelse(pbsc[,"bbu"]>0,"gold2",
                                     ifelse(pbsc[,4]>col[1],"green2",as.factor(pbsc[,1])))))),
     xlab="",xaxt='n',cex.lab=1,cex.axis=2.2,bty="n",ylim=c(-.5,3.8),yaxs="i")

plot(pbsc[,5],pch=20,cex=1.2,
     col=ifelse(pbsc[,"all"]>0,"purple",
                ifelse(pbsc[,"res"]>0,"black",
                       ifelse(pbsc[,"interm"]>0,"firebrick2",
                              ifelse(pbsc[,"vbu"]>0,"gold2",
                                     ifelse(pbsc[,5]>col[2],"green2",as.factor(pbsc[,1])))))),
     xlab="",xaxt='n',cex.lab=1,cex.axis=2.2,bty="n",ylim=c(-.5,3.8),yaxs="i")

plot(pbsc[,6],pch=20,cex=1.2,
     col=ifelse(pbsc[,"all"]>0,"purple",
                ifelse(pbsc[,"res"]>0,"black",
                       ifelse(pbsc[,"interm"]>0,"firebrick2",
                              ifelse(pbsc[,"pbu"]>0,"gold2",
                                     ifelse(pbsc[,6]>col[3],"green2",as.factor(pbsc[,1])))))),
     xlab="",xaxt='n',cex.lab=1,cex.axis=2.2,bty="n",ylim=c(-.5,3.8),yaxs="i")

plot(pbsc[,7],pch=20,cex=1.2,
     col=ifelse(pbsc[,"all"]>0,"purple",
                ifelse(pbsc[,"res"]>0,"black",
                       ifelse(pbsc[,"interm"]>0,"firebrick2",
                              ifelse(pbsc[,"sju"]>0,"gold2",
                                     ifelse(pbsc[,7]>col[4],"green2",as.factor(pbsc[,1])))))),
     xlab="",xaxt='n',cex.lab=1,cex.axis=2.2,bty="n",ylim=c(-.5,3.8),yaxs="i")

plot(pbsc[,8],pch=20,cex=1.2,
     col=ifelse(pbsc[,"all"]>0,"purple",
                ifelse(pbsc[,"res"]>0,"black",
                       ifelse(pbsc[,"interm"]>0,"firebrick2",
                              ifelse(pbsc[,"bnpu"]>0,"gold2",
                                     ifelse(pbsc[,8]>col[5],"green2",as.factor(pbsc[,1])))))),
     xlab="",xaxt='n',cex.lab=1,cex.axis=2.2,bty="n",ylim=c(-.5,3.8),yaxs="i")

#Simplified to fewer outliers----

pbsc$Scaf<-factor(pbsc$Scaf,levels=c("chr1","chr2","chr3","chr4","chr5","chr6","chr7","chr8","chr9","chr10",
                                     "chr11","chr12","chr13","chr14","chr15","chr16","chr17","chr18","chr19",
                                     "chr20","chr21","chr22","chr23","chr24"))
palette(c("grey40","grey80"))
par(mfrow=c(5,1),mar=c(0,3,0,0))
plot(pbsc[,4],pch=20,cex=1.2,
     col=ifelse(pbsc[,"all"]>0,"purple",
                ifelse(pbsc[,"res"]>0,"black",
                       ifelse(pbsc[,"interm"]>0,"firebrick2",
                              as.factor(pbsc[,1])))),
     xlab="",xaxt='n',cex.lab=1,cex.axis=2.2,bty="n",ylim=c(-.5,3.8),yaxs="i")

plot(pbsc[,5],pch=20,cex=1.2,
     col=ifelse(pbsc[,"all"]>0,"purple",
                ifelse(pbsc[,"res"]>0,"black",
                       ifelse(pbsc[,"interm"]>0,"firebrick2",
                            as.factor(pbsc[,1])))),
     xlab="",xaxt='n',cex.lab=1,cex.axis=2.2,bty="n",ylim=c(-.5,3.8),yaxs="i")

plot(pbsc[,6],pch=20,cex=1.2,
     col=ifelse(pbsc[,"all"]>0,"purple",
                ifelse(pbsc[,"res"]>0,"black",
                       ifelse(pbsc[,"interm"]>0,"firebrick2",
                              as.factor(pbsc[,1])))),
     xlab="",xaxt='n',cex.lab=1,cex.axis=2.2,bty="n",ylim=c(-.5,3.8),yaxs="i")

plot(pbsc[,7],pch=20,cex=1.2,
     col=ifelse(pbsc[,"all"]>0,"purple",
                ifelse(pbsc[,"res"]>0,"black",
                       ifelse(pbsc[,"interm"]>0,"firebrick2",
                              as.factor(pbsc[,1])))),
     xlab="",xaxt='n',cex.lab=1,cex.axis=2.2,bty="n",ylim=c(-.5,3.8),yaxs="i")

plot(pbsc[,8],pch=20,cex=1.2,
     col=ifelse(pbsc[,"all"]>0,"purple",
                ifelse(pbsc[,"res"]>0,"black",
                       ifelse(pbsc[,"interm"]>0,"firebrick2",
                              as.factor(pbsc[,1])))),
     xlab="",xaxt='n',cex.lab=1,cex.axis=2.2,bty="n",ylim=c(-.5,3.8),yaxs="i")

```

## Breaking these up into 1kb windows and observing whether they are unique

```{r}
###Plotting outliers vs each other-----------
pbsct<-pbs %>% filter(str_detect(Scaf,"chr")) #getting only scaffolds mapped onto chromosomes here

pbsc<-na.omit(pbsc[,1:8]) #removing NA values from them

#checking for whether those are outliers in different groups
all<-pbsc[,4]>col[1] & pbsc[,5]>col[2] & pbsc[,6]>col[3] & pbsc[,7]>col[4] & pbsc[,8]>col[5]
res<-pbsc[,4]>col[1] & pbsc[,5]>col[2] & pbsc[,6]>col[3] & pbsc[,7]<col[4] & pbsc[,8]<col[5]
interm<-pbsc[,4]<col[1] & pbsc[,5]<col[2] & pbsc[,6]<col[3] & pbsc[,7]>col[4] & pbsc[,8]>col[5]
bbu<-pbsc[,4]>col[1] & pbsc[,5]<col[2] & pbsc[,6]<col[3] & pbsc[,7]<col[4] & pbsc[,8]<col[5]
vbu<-pbsc[,4]<col[1] & pbsc[,5]>col[2] & pbsc[,6]<col[3] & pbsc[,7]<col[4] & pbsc[,8]<col[5]
pbu<-pbsc[,4]<col[1] & pbsc[,5]<col[2] & pbsc[,6]>col[3] & pbsc[,7]<col[4] & pbsc[,8]<col[5]
sju<-pbsc[,4]<col[1] & pbsc[,5]<col[2] & pbsc[,6]<col[3] & pbsc[,7]>col[4] & pbsc[,8]<col[5]
bnpu<-pbsc[,4]<col[1] & pbsc[,5]<col[2] & pbsc[,6]<col[3] & pbsc[,7]<col[4] & pbsc[,8]>col[5]

#as before, checking which of those regions of divergence maps to specific windows of divergence
write.table(pbsc[,1:3],"~/analysis/data/fst/subsample/PBS_keep_1kb.bed",row.names = FALSE,col.names = FALSE,quote=FALSE,sep='\t')
write.table(na.omit(pbsc[all,1:3]),"~/analysis/data/fst/subsample/pbs_regions_sharedall.bed",row.names = FALSE,col.names = FALSE,quote = FALSE,sep='\t')
write.table(na.omit(pbsc[res,1:3]),"~/analysis/data/fst/subsample/pbs_regions_sharedres.bed",row.names = FALSE,col.names = FALSE,quote = FALSE,sep='\t')
write.table(na.omit(pbsc[interm,1:3]),"~/analysis/data/fst/subsample/pbs_regions_sharedinterm.bed",row.names = FALSE,col.names = FALSE,quote = FALSE,sep='\t')
write.table(na.omit(pbsc[bbu,1:3]),"~/analysis/data/fst/subsample/pbs_regions_sharedbbu.bed",row.names = FALSE,col.names = FALSE,quote = FALSE,sep='\t')
write.table(na.omit(pbsc[vbu,1:3]),"~/analysis/data/fst/subsample/pbs_regions_sharedvbu.bed",row.names = FALSE,col.names = FALSE,quote = FALSE,sep='\t')
write.table(na.omit(pbsc[pbu,1:3]),"~/analysis/data/fst/subsample/pbs_regions_sharedpbu.bed",row.names = FALSE,col.names = FALSE,quote = FALSE,sep='\t')
write.table(na.omit(pbsc[sju,1:3]),"~/analysis/data/fst/subsample/pbs_regions_sharedsju.bed",row.names = FALSE,col.names = FALSE,quote = FALSE,sep='\t')
write.table(na.omit(pbsc[bnpu,1:3]),"~/analysis/data/fst/subsample/pbs_regions_sharedbnpu.bed",row.names = FALSE,col.names = FALSE,quote = FALSE,sep='\t')


#source("http://bioconductor.org/biocLite.R")
#biocLite()
#biocLite('rtracklayer')

#Finding the overlaps in full data---------
library("rtracklayer")

#summarizing these outlier windows, instead of by regions, by 1kb windows - look behind if confused about script (previous chunk)
bed1=import("~/analysis/data/fst/subsample/PBS_keep_1kb.bed")

bedall=import("~/analysis/data/fst/subsample/pbs_regions_sharedall.bed")
bed1overlall=bed1[bed1 %over% bedall]
hitsall<-findOverlaps(bedall,bed1)
allhit<-subjectHits(hitsall)

bedres=import("~/analysis/data/fst/subsample/pbs_regions_sharedres.bed")
bed1overlres=bed1[bed1 %over% bedres]
hitsres<-findOverlaps(bedres,bed1)
reshit<-subjectHits(hitsres)

bedinterm=import("~/analysis/data/fst/subsample/pbs_regions_sharedinterm.bed")
bed1overlinterm=bed1[bed1 %over% bedinterm]
hitsinterm<-findOverlaps(bedinterm,bed1)
intermhit<-subjectHits(hitsinterm)

bedbbu=import("~/analysis/data/fst/subsample/pbs_regions_sharedbbu.bed")
bed1overlbbu=bed1[bed1 %over% bedbbu]
hitsbbu<-findOverlaps(bedbbu,bed1)
bbuhit<-subjectHits(hitsbbu)

bedvbu=import("~/analysis/data/fst/subsample/pbs_regions_sharedvbu.bed")
bed1overlvbu=bed1[bed1 %over% bedvbu]
hitsvbu<-findOverlaps(bedvbu,bed1)
vbuhit<-subjectHits(hitsvbu)

bedpbu=import("~/analysis/data/fst/subsample/pbs_regions_sharedpbu.bed")
bed1overlpbu=bed1[bed1 %over% bedpbu]
hitspbu<-findOverlaps(bedpbu,bed1)
pbuhit<-subjectHits(hitspbu)

bedsju=import("~/analysis/data/fst/subsample/pbs_regions_sharedsju.bed")
bed1overlsju=bed1[bed1 %over% bedsju]
hitssju<-findOverlaps(bedsju,bed1)
sjuhit<-subjectHits(hitssju)

bedbnpu=import("~/analysis/data/fst/subsample/pbs_regions_sharedbnpu.bed")
bed1overlbnpu=bed1[bed1 %over% bedbnpu]
hitsbnpu<-findOverlaps(bedbnpu,bed1)
bnpuhit<-subjectHits(hitsbnpu)

pbsc<-cbind(pbsc,0,0,0,0,0,0,0,0) #adding these to the 1kb windows we've separated the genome into
newn<-c("Scaf","start","end","BB","VB","PB","SJ","BNP","all","res","interm","bbu","vbu","pbu","sju","bnpu")
colnames(pbsc)<-newn
pbsc[allhit,"all"]<-pbsc[allhit,"all"]+1 #naming adding +1 to each of those windows that is shared
pbsc[reshit,"res"]<-pbsc[reshit,"res"]+1
pbsc[intermhit,"interm"]<-pbsc[intermhit,"interm"]+1
pbsc[bbuhit,"bbu"]<-pbsc[bbuhit,"bbu"]+1
pbsc[vbuhit,"vbu"]<-pbsc[vbuhit,"vbu"]+1
pbsc[pbuhit,"pbu"]<-pbsc[pbuhit,"pbu"]+1
pbsc[sjuhit,"sju"]<-pbsc[sjuhit,"sju"]+1
pbsc[bnpuhit,"bnpu"]<-pbsc[bnpuhit,"bnpu"]+1

par(mfrow=c(2,3),mar=c(4,4,0,0)) #plotting these outlier windows vs each other for each population to see how they are distributed among resistant and intermediate populations
plot(pbsc[,"BB"],pbsc[,"VB"],pch=20,cex=.7,
     col=ifelse(pbsc[,"all"]>0,"purple",
                ifelse(pbsc[,"interm"]>0,"red",
                       ifelse(pbsc[,"res"],"black",NA))),bty='l',
     xlab="VB z values",ylab="BB z values")
abline(h=0,v=0)

plot(pbsc[,"BB"],pbsc[,"PB"],pch=20,cex=.7,
     col=ifelse(pbsc[,"all"]>0,"purple",
                ifelse(pbsc[,"interm"]>0,"red",
                       ifelse(pbsc[,"res"],"black",NA))),bty='l',
     xlab="PB z values",ylab="BB z values")
abline(h=0,v=0)

plot(pbsc[,"VB"],pbsc[,"PB"],pch=20,cex=.7,
     col=ifelse(pbsc[,"all"]>0,"purple",
                ifelse(pbsc[,"interm"]>0,"red",
                       ifelse(pbsc[,"res"],"black",NA))),bty='l',
     xlab="PB z values",ylab="VB z values")
abline(h=0,v=0)

plot(pbsc[,"SJ"],pbsc[,"PB"],pch=20,cex=.7,
     col=ifelse(pbsc[,"all"]>0,"purple",
                ifelse(pbsc[,"interm"]>0,"red",
                       ifelse(pbsc[,"res"],"black",NA))),bty='l',
     xlab="PB z values",ylab="SJ z values")
abline(h=0,v=0)

plot(pbsc[,"BNP"],pbsc[,"PB"],pch=20,cex=.7,
     col=ifelse(pbsc[,"all"]>0,"purple",
                ifelse(pbsc[,"interm"]>0,"red",
                       ifelse(pbsc[,"res"],"black",NA))),bty='l',
     xlab="PB z values",ylab="BNP z values")
abline(h=0,v=0)

plot(pbsc[,"BNP"],pbsc[,"SJ"],pch=20,cex=.7,
     col=ifelse(pbsc[,"all"]>0,"purple",
                ifelse(pbsc[,"interm"]>0,"red",
                       ifelse(pbsc[,"res"],"black",NA))),bty='l',
     xlab="SJ z values",ylab="BNP z values")
abline(h=0,v=0)
```

##Test for finding if they are truly different by simulating 1000 random regions of the same size from the genome

```{r}

intermeans<-c()
for(i in 1:5){
  intermeans[i]<-mean(pbsc[interm,i+3],na.rm=TRUE)
}

resmeans<-c()
for(i in 1:5){
  resmeans[i]<-mean(pbsc[res,i+3],na.rm=TRUE)
}

allmeans<-c()
for(i in 1:5){
  allmeans[i]<-mean(pbsc[all,i+3],na.rm=TRUE)
}

#plotting histogram for intermediate regions----
rimeans<-c()
b<-c()
for(i in 1:5){
  for(j in 1:1000){
    b[j]<-mean(sample(pbsc[,i+3],size=765,replace=FALSE))
  }
  rimeans<-cbind(rimeans,b)
}

nam<-c("BB","VB","PB","SJ","BNP")
colnames(rimeans)<-nam
cols<-c("black","black","black","firebrick2","firebrick2")

par(mfrow=c(2,3),mar=c(4,4,2,2))
for(i in 1:length(nam)){
  hist(rimeans[,i],main='',breaks=30,xlim=c(range(rimeans[,i]-.1,na.rm=TRUE)[[1]],intermeans[i]+.5),
       bty='l',col=cols[i],border=cols[i],xlab=nam[i],cex.axis=3,ylab='')
  abline(v=intermeans[i],lwd=3,col="green")
  box(bty='l',lwd=3)
}

#plotting histogram for resistant only regions----

rrmeans<-c()
b<-c()
for(i in 1:5){
  for(j in 1:1000){
    b[j]<-mean(sample(pbsc[,i+3],size=2549,replace=FALSE))
  }
  rrmeans<-cbind(rrmeans,b)
}

nam<-c("BB","VB","PB","SJ","BNP")
colnames(rrmeans)<-nam
cols<-c("black","black","black","firebrick2","firebrick2")

par(mfrow=c(2,3))
for(i in 1:length(nam)){
  hist(rrmeans[,i],main='',breaks=30,xlim=c(range(rrmeans[,i]-.1,na.rm=TRUE)[[1]],resmeans[i]+.5),
       bty='l',col=cols[i],border=cols[i],xlab=nam[i])
  abline(v=resmeans[i],lwd=3,col="green")
}

###plotting histogram for shared regions----

rameans<-c()
b<-c()
for(i in 1:5){
  for(j in 1:1000){
    b[j]<-mean(sample(pbsc[,i+3],size=259,replace=FALSE))
  }
  rameans<-cbind(rameans,b)
}

nam<-c("BB","VB","PB","SJ","BNP")
colnames(rameans)<-nam
cols<-c("black","black","black","firebrick2","firebrick2")

par(mfrow=c(2,3))
for(i in 1:length(nam)){
  hist(rameans[,i],main='',breaks=30,xlim=c(range(rameans[,i]-.1,na.rm=TRUE)[[1]],allmeans[i]+.5),
       bty='l',col=cols[i],border=cols[i],xlab=nam[i])
  abline(v=allmeans[i],lwd=3,col="green")
}


```


## Plotting specific regions of the genome based on divergence - messed up for now, will have to re-do

```{r}
#smoothing funciton----
subsmooth <- function(vec,by=10,width=11){
  
  len <- length(vec)
  subl <- seq(from=by,to=len,by=by)
  submax <- length(subl)
  width <- width/2
  test <- vec[subl]
  
  for(i in 1:submax){
    
    j <- i - width
    k <- i + width
    if(j < 1) {j <- 1}
    if(k > submax) {k <- submax}
    test[i] <- mean(test[j:k],na.rm=TRUE)
  }
  
  return(test)
  
}


###Plotting CHR1/AHR region------------
pbsc1<-pbsc %>% filter(str_detect(Scaf,"\\bchr1\\b"))

par(mfrow=c(5,1),mar=c(3,3,0,0),mgp=c(1,1,0))

for(i in 1:5){
  plot(subsmooth(pbsc1[1:5000,i+3]),pch=20,cex=.5,ylim=c(0,1.8),bty='l',cex.axis=2,ylab='',xlab='')
  box(bty='l',lwd=3)
  abline(v=c(50,60),col="red",lty=2,lwd=1.5)
}

#plotting ARNT chr8----
pbsc8<-pbsc %>% filter(str_detect(Scaf,"\\bchr8\\b"))

par(mfrow=c(5,1),mar=c(3,3,0,0),mgp=c(1,1,0))

for(i in 1:5){
  plot(subsmooth(pbsc8[14000:18000,i+3]),pch=20,cex=.5,ylim=c(0,.5),bty='l',cex.axis=2,ylab='',xlab='')
  box(bty='l',lwd=3)
  abline(v=c(170,173),col="red",lty=2,lwd=1.5)
}


#plotting AIP chr2----
pbsc2<-pbsc %>% filter(str_detect(Scaf,"\\bchr2\\b"))

par(mfrow=c(5,1),mar=c(3,3,0,0),mgp=c(1,1,0))

for(i in 1:5){
  plot(subsmooth(pbsc2[23000:26000,i+3]),pch=20,cex=.5,ylim=c(0,.4),bty='l',cex.axis=2,ylab='',xlab='')
  box(bty='l',lwd=3)
  abline(v=c(140,142),col="red",lty=2,lwd=1.5)
}

#plotting AQP3

pbsc24<-pbsc %>% filter(str_detect(Scaf,"\\bchr24\\b"))

par(mfrow=c(5,1),mar=c(3,3,0,0),mgp=c(1,1,0))

for(i in 1:5){
  plot(subsmooth(pbsc24[22000:26000,i+3]),pch=20,cex=.5,ylim=c(0,.5),bty='l',cex.axis=2,ylab='',xlab='')
  box(bty='l',lwd=3)
  abline(v=c(159,162),col="red",lty=2,lwd=1.5)
}

#plotting AQP3

pbsc11<-pbsc %>% filter(str_detect(Scaf,"\\bchr11\\b"))

par(mfrow=c(5,1),mar=c(3,3,0,0),mgp=c(1,1,0))

for(i in 1:5){
  plot(subsmooth(pbsc11[27000:28940,i+3]),pch=20,cex=.5,ylim=c(0,.5),bty='l',cex.axis=2,ylab='',xlab='')
  box(bty='l',lwd=3)
  abline(v=c(181,188),col="red",lty=2,lwd=1.5)
}

```

##Calculating Hudson's Fst from pi and dxy

```{r}
load("~/analysis/data/comparison/noah_stats.RData") #loading data produced from individual SNP call pi and dxy calculations

pops<-c("BB","VB","PB","SJSP","BNP","GB","SP") #creating a vector of names for our populations

fsth<-as.data.frame(fst[,1:21])#creating matrix to hold fst data takes about 1 hour to run; Here I'm calculating Hudson's Fst from our dataset;

f=0
for(i in pops){
  for(j in pops){
    if(i==j){next()}
    if(i>j){next()}
    f<-f+1
    print(f)
    colnames(fsth)[f]<-paste(sort(unique(c(i,j))),collapse=".")
    print(colnames(fsth)[f])
    fsth[,f]<-1-((fst[,i]+fst[,j])/2)/fst[,paste(sort(unique(c(i,j))),collapse=".")]
  }
}

#write.table(fsth,"~/analysis/data/fst/fsth",col.names = FALSE,quote = FALSE,row.names = FALSE) #to save it for later

#fsth<-read.table("~/analysis/data/fst/fsth",header=FALSE) #loading fsth values
```
##Caclulating Z statistic from the fst values

```{r}
#Dependent on having loaded fsth into RAM from above chunk
# install.packages('matrixStats')
library(matrixStats)

fsth[!is.finite(as.matrix(fsth))]<-NA #making all inifite values into NA

fstmeans<-colMeans(fsth,na.rm=TRUE) #calculating average fst
fstmeans<-as.matrix(fstmeans) #putting it into a matrix

fststdev<-colSds(as.matrix(fsth),na.rm=TRUE) #calculating standard deviation overall
fststdev<-as.matrix(fststdev)
row.names(fststdev)<-row.names(fstmeans) #making sure the rows are correctly assigned

zfst<-matrix(nrow=dim(fsth)[1],ncol=dim(fsth)[2]) #creating a matrix that will hold z values
colnames(zfst)<-colnames(fsth)

#running a loop that calculates z values
for (i in 1:21){
    zfst[,i]<-(fsth[,i]-fstmeans[i])/fststdev[i]
}

#write.table(zfst,"~/analysis/data/fst/zfst_hud_1kb",row.names=FALSE,col.names=FALSE,quote=FALSE,sep="\t")
#zfst<-read.table("~/analysis/data/fst/zfst_hud_1kb",header=FALSE)
```

##Subtraction of pi and conversion to z statistic CORRECT THIS TO BE THE PI VALUES YOU JUST CALCULATED FROM ANGSD

```{r}
pi<-cbind(fst[,"BB"],fst[,"VB"],fst[,"PB"],fst[,"SJSP"],fst[,"BNP"],fst[,"GB"],fst[,"SP"]) #taking only pi values for F. grandis from dataframe
pops<-c("BB","VB","PB","SJSP","BNP","GB","SP") #creating a vector of names for our populations
colnames(pi)<-c(pops)

head(val) # vector of # of SNPs evaluated to come to a summary statistic per window

pib<-pi/val[,4] #converting these estimates to per base
pib[!is.finite(as.matrix(pib))]<-NA #putting NA in the stead of all all infinite values

pidiff<-as.data.frame(fst[,1:21]) #creating data frame that would hold pidiff values

#looping over variables to calculate the difference in pi
f=0
for(i in pops){
  for(j in pops){
    if(i==j){next()}
    if(i>j){next()}
    f<-f+1
    print(f)
    colnames(pidiff)[f]<-paste(sort(unique(c(i,j))),collapse=".")
    print(colnames(pidiff)[f])
    pidiff[,f]<-pib[,i]-pib[,j]
  }
}

pidiff[!is.finite(as.matrix(pidiff))]<-NA #removing all infinite values and replacing with NA
pimeans<-colMeans(as.matrix(pidiff),na.rm=TRUE) #calculating means of columns of pi difference
pimeans<-as.matrix(pimeans) #converting into a matrix so I can use numeric values out of it

library(matrixStats)
pistdev<-colSds(as.matrix(pidiff),na.rm=TRUE) #calculating standard deviation from columns
pistdev<-as.matrix(pistdev)

zpi<-matrix(nrow=dim(pidiff)[[1]],ncol = dim(pidiff)[[2]])

for (i in 1:21){
    zpi[,i]<-(pidiff[,i]-pimeans[i])/pistdev[i]
}
colnames(zpi)<-colnames(pidiff)

#write.table(zpi,"~/analysis/data/angsd/zpi_1kb",row.names = FALSE,col.names = FALSE,quote = FALSE,sep='\t')
```

##Messing around with pi

```{r}

mpi<-melt(pib[,1:7])

ggplot(mpi,
       aes(x=Var2,y=value,fill=Var2,color=Var2))+
  geom_violin(trim=FALSE,draw_quantiles = 0.5,lwd=2)+
  scale_fill_manual(values=c("black","grey40","grey80","firebrick2","lightpink","cadetblue1","cadetblue3"))+
  scale_color_manual(values=c("grey40",rep("black",6)))+
  scale_y_continuous(limits=c(0,.017))+
  theme_classic()+
  labs(y="",x="")+
  theme(axis.line.y=element_line(color="black",size=5),axis.line=element_line(color="black",size=5))+
  theme(axis.text.y=element_text(color="black",size=40))


```

## Merging z statistics into a common one (high z would mean high fst and low pi)

```{r}
#zfst<-read.table("~/analysis/data/fst/zfst_hud_1kb",sep='\t')
#zpi<-read.table("~/analysis/data/angsd/zpi_1kb",sep="\t")
colnames(zfst)<-colnames(fsth) #naming columns
colnames(zpi)<-colnames(fsth)

zfst<-as.data.frame(zfst)
zpi<-as.data.frame(zpi)

zfst2<-zfst %>% mutate(seq=seq(1:dim(zfst)[[1]])) #adding sequence, basically a way to match the rows to each other
zpi2<-zpi %>% mutate(seq=seq(1:dim(zpi)[[1]])) #same

colnam<-colnames(zfst2[,1:21]) #saving colnames as a vector so we can match columns
zmerge_temp<-cbind(zfst2[colnam]-zpi2[match(zfst2$seq,zpi2$seq),colnam]) #subtracting zpi from zfst for a zmerge

subw<-val[,4]>5 #filtering values that didn't have very many supportive snps

zmerge<-zmerge_temp %>% mutate(keep=as.numeric(subw)) #Adds that filter column as 0s and 1s

#write.table(zmerge,"~/analysis/data/dfst/zmerge_1kb",row.names = FALSE,col.names = FALSE,quote = FALSE)

```

## Doing a PBS analysis with Z statistics

```{r}
#zmerge<-read.table("~/analysis/data/dfst/zmerge_1kb",header=FALSE)

znames<-c(names(fsth),"keep")
colnames(zmerge)<-znames

names(zmerge)<-gsub("SJSP","SJ",names(zmerge))

distgb<-zmerge %>% 
  select(contains("GB")) #only selecting GB columns
sub1<-gsub("GB.","",names(distgb)) #removing GB from names
sub2<-gsub(".GB","",sub1)
names(distgb)<-sub2

distsp<-zmerge %>% 
  select(contains("SP")) #only selecting SP columns
sub3<-gsub("SP.","",names(distsp))
sub4<-gsub(".SP","",sub3)
names(distsp)<-sub4

pops<-c("BB","VB","PB","SJ","BNP")

distgb2<-distgb %>% 
  select(pops) #rearranging columns

distsp2<-distsp %>% 
  select(pops)

colnam<-colnames(distgb2) #assigning a vector
distsp3<-distsp2 %>% mutate(seq=seq(1:dim(distsp)[[1]])) #adding sequence as before
distgb3<-distgb2 %>% mutate(seq=seq(1:dim(distgb)[[1]]))

total_dist<-cbind(distsp3[colnam]+distgb3[match(distsp3$seq,distgb3$seq),colnam]) #matching the two and adding them to each

pbsz<-matrix(nrow=dim(total_dist)[[1]],ncol=dim(total_dist)[[2]]) #creating matriz to hold 

for(i in 1:5){ #calculating the z pbs value
  pbsz[,i]<-(total_dist[,i]-distgb[,"SP"])/2
}
colnames(pbsz)<-colnames(total_dist)#naming

subw<-val[,4]>20 #filter

plot(pbsz[subw,"PB"],pch=20,cex=.2,ylim=c(-10,30))

zpbs<-cbind(lift,pbsz) #plugging in location values

ord<-mixedorder(zpbs$V1) #Data imported is ordered alphabetically (ex. chr1, chr10...); this reorders it to alphanumeric (chr1, chr2...)
zpbsn<-zpbs[ord,] #applying sorted order to our dataset

write.table(zpbsn,"~/analysis/data/dfst/zpbs_1kb",row.names = FALSE,col.names = FALSE,quote = FALSE,sep="\t") #writing

```

##Looking at 1% outlier regions

```{r}
col<-c() #figuring outliers
for (i in 1:5){
  col[i]<-quantile(zpbs[,i+3],prob=.99,na.rm=TRUE)
}
names(col)<-names(total_dist)
#1% thresholds
print(col)

```

##Creating outlier regions of interest

```{bash}
cat ~/analysis/data/dfst/zpbs_1kb | grep -v NA | \
awk '$4>3.523703 || $5>3.172488  || $6>3.340705 || $7>3.031223 || $8>2.910434' | \
~/program/bedtools2/bin/bedtools merge -i stdin -d 50000 \
-c 4,4,5,5,6,6,7,7,8,8 \
-o max,count,max,count,max,count,max,count,max,count \
-g <(cut -f 1-2 ~/analysis/data/genome/unsplit_merge.fasta.fai) > ~/analysis/data/dfst/zregions_max_1kb.bed
```

#Now let's plot up some figures with the merged z statistics

```{r}
zpbs<-zpbsn %>% 
  filter(str_detect(V1,"chr")) #filtering only chromosome mapped regions

#using data from the outlier regions in order to select regions of interest that are shared, res unique or interm unique
pbs_out_temp<-read.table("~/analysis/data/dfst/zregions_max_1kb.bed",stringsAsFactors = FALSE) #loads a pbs vector with windows merged within 50kb of each other and with max and windows count statistics
names<-c("Scaf","start","end","BBmax","BBcount","VBmax","VBcount","PBmax","PBcount","SJmax","SJcount","BNPmax","BNPcount") #naming columns
colnames(pbs_out_temp)<-names

pbs_out<-pbs_out_temp %>% filter(str_detect(Scaf,"chr")) #filtering to only select chromosome mapped scaffolds

all<-pbs_out[,4]>col[1] & pbs_out[,6]>col[2] & pbs_out[,8]>col[3] & pbs_out[,10]>col[4] & pbs_out[,12]>col[5] # vector wiht T/F of shared outliers
res<-pbs_out[,4]>col[1] & pbs_out[,6]>col[2] & pbs_out[,8]>col[3] & pbs_out[,10]<col[4] & pbs_out[,12]<col[5]
interm<-pbs_out[,4]<col[1] & pbs_out[,6]<col[2] & pbs_out[,8]<col[3] & pbs_out[,10]>col[4] & pbs_out[,12]>col[5]

write.table(lift[,1:3],"~/analysis/data/dfst/zpbs.bed",row.names = FALSE,col.names = FALSE,quote=FALSE, sep="\t") #saving background genomic regions in bed format
write.table(pbs_out[all,1:3],"~/analysis/data/dfst/pbs_regions_sharedall.bed",row.names = FALSE,col.names = FALSE,quote = FALSE,sep="\t") #saving shared regions to look at overlap with the 1kb regions
write.table(pbs_out[res,1:3],"~/analysis/data/dfst/pbs_regions_sharedres.bed",row.names = FALSE,col.names = FALSE,quote = FALSE,sep="\t")
write.table(pbs_out[interm,1:3],"~/analysis/data/dfst/pbs_regions_sharedinterm.bed",row.names = FALSE,col.names = FALSE,quote = FALSE,sep="\t")

#only run source() and biocLite() if you don't have them installed
# source("http://bioconductor.org/biocLite.R")
# biocLite()
library("rtracklayer")

bed1=import("~/analysis/data/dfst/zpbs.bed")

bedall=import("~/analysis/data/dfst/pbs_regions_sharedall.bed")
bed1overlall=bed1[bed1 %over% bedall]
hitsall<-findOverlaps(bedall,bed1)
allhit<-subjectHits(hitsall)

bedres=import("~/analysis/data/dfst/pbs_regions_sharedres.bed")
bed1overlres=bed1[bed1 %over% bedres]
hitsres<-findOverlaps(bedres,bed1)
reshit<-subjectHits(hitsres)

bedinterm=import("~/analysis/data/dfst/pbs_regions_sharedinterm.bed")
bed1overlinterm=bed1[bed1 %over% bedinterm]
hitsinterm<-findOverlaps(bedinterm,bed1)
intermhit<-subjectHits(hitsinterm)

zpbs<-cbind(zpbs,0,0,0)
newn<-c("Scaf","start","end","BB","VB","PB","SJ","BNP","all","res","interm")
colnames(zpbs)<-newn
zpbs[allhit,"all"]<-zpbs[allhit,"all"]+1
zpbs[reshit,"res"]<-zpbs[reshit,"res"]+1
zpbs[intermhit,"interm"]<-zpbs[intermhit,"interm"]+1

zpbs$Scaf<-factor(zpbs$Scaf,levels=c("chr1","chr2","chr3","chr4","chr5","chr6","chr7","chr8","chr9","chr10",
                                     "chr11","chr12","chr13","chr14","chr15","chr16","chr17","chr18","chr19",
                                     "chr20","chr21","chr22","chr23","chr24")) #factors are sometimes not sorted together with it, so sorting them separately

palette(c("grey40","grey80"))
par(mfrow=c(5,1),mar=c(0,3,0,0))
plot(zpbs[,4],pch=20,cex=1.2,
     col=ifelse(zpbs[,"all"]>0,"purple",
                ifelse(zpbs[,"res"]>0,"black",
                       ifelse(zpbs[,"interm"]>0,"firebrick2",sort(as.factor(zpbs[,1]))))),
     xlab="",xaxt='n',cex.lab=1,cex.axis=2.2,bty="n",ylim=c(-40,40),yaxs="i")

plot(zpbs[,5],pch=20,cex=1.2,
     col=ifelse(zpbs[,"all"]>0,"purple",
                ifelse(zpbs[,"res"]>0,"black",
                       ifelse(zpbs[,"interm"]>0,"firebrick2",sort(as.factor(zpbs[,1]))))),
     xlab="",xaxt='n',cex.lab=1,cex.axis=2.2,bty="n",ylim=c(-40,40),yaxs="i")

plot(zpbs[,6],pch=20,cex=1.2,
     col=ifelse(zpbs[,"all"]>0,"purple",
                ifelse(zpbs[,"res"]>0,"black",
                       ifelse(zpbs[,"interm"]>0,"firebrick2",sort(as.factor(zpbs[,1]))))),
     xlab="",xaxt='n',cex.lab=1,cex.axis=2.2,bty="n",ylim=c(-40,40),yaxs="i")

plot(zpbs[,7],pch=20,cex=1.2,
     col=ifelse(zpbs[,"all"]>0,"purple",
                ifelse(zpbs[,"res"]>0,"black",
                       ifelse(zpbs[,"interm"]>0,"firebrick2",sort(as.factor(zpbs[,1]))))),
     xlab="",xaxt='n',cex.lab=1,cex.axis=2.2,bty="n",ylim=c(-40,40),yaxs="i")

plot(zpbs[,8],pch=20,cex=1.2,
     col=ifelse(zpbs[,"all"]>0,"purple",
                ifelse(zpbs[,"res"]>0,"black",
                       ifelse(zpbs[,"interm"]>0,"firebrick2",sort(as.factor(zpbs[,1]))))),
     xlab="",xaxt='n',cex.lab=1,cex.axis=2.2,bty="n",ylim=c(-40,40),yaxs="i")

```
